---
title: "Estimate"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEnry{Estimate}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Introduction

Estimating the the models described in Explaining Recruitment to Violent Extremism: A Bayesian Case-Control Approach (ERVE) requires just two steps:

1. Prepare the data sources in list format using `data.prep()`
2. Estimate the model using `fit()`

This explainer vignette walks you through the second of these two steps.

## Setup

First install the package from source if not already installed.

```{r, eval =FALSE}
devtools::install_github("cjbarrie/extremeR")
```

We then load the package into memory as follows.

```{r, warning = F, message = F}
library(extremeR)
```

## Load data

Then we load the pre-formatted data into memory as follows.

```{r, eval = F}
data(data.list)
```

```{r, echo = F}
load("data/data.list.rda")
```

## Estimate model 

And we are then ready to estimate the ERVE model for the Egyptian case-control data.

The `fitp()` function has a series of parameters that we tabulate and describe below.

| Argument   |     Description      |
|----------|:-------------:|
|data | list, survey and shapefile combined list object created with the `data.prep()` function
|show_code | logical, should the stan code print on the screen at the end of the run? Defaults to `TRUE`
|contamination | logical, should the model include the Rota et al. (2013) style contamination layer? Defaults to `TRUE`
|offset | logical, should the model include a King and Zeng (2001) style offset ? if contamination is also specified, this will be a contaminated-offset. Defaults to `TRUE`
|beta_prior | string, what prior should the regression coefficients have? Choice between: "normal" and "cauchy"
|small_area_prior | string, what should be the small-area effects type? Choice between: "fixed," "random," "ICAR," and "BYM2." Specify `NA` for no area effects. Defaults to "fixed"
|large_area_prior | string, what should be the large-area effects type? Choice between: "fixed" and "random." Specify `NA` for no area effects. Defaults to `NA`.
|intercept_scale | integer, scale of intercept; arguments taken from `rstan`, see [here](https://mc-stan.org/users/interfaces/rstan) for further information
|iter | integer, number of draws; arguments taken from `rstan`, see [here](https://mc-stan.org/users/interfaces/rstan) for further information
|warmup | integer, number of warmup draws; arguments taken from `rstan`, see [here](https://mc-stan.org/users/interfaces/rstan) for further information
|thin | integer, number to thin draws; arguments taken from `rstan`, see [here](https://mc-stan.org/users/interfaces/rstan) for further information
|cores | integer, number of cores to use; arguments taken from `rstan`, see [here](https://mc-stan.org/users/interfaces/rstan) for further information
|chains | integer, number of chains; arguments taken from `rstan`, see [here](https://mc-stan.org/users/interfaces/rstan) for further information
|control | list, tree depth and adapt delta; arguments taken from `rstan`, see [here](https://mc-stan.org/users/interfaces/rstan) for further information
|verbose | logical, print full stan output? Defaults to `TRUE`

```{r, eval = F}
fit_object = fit(
  data = data.list,
  show_code = T,
  contamination = T,
  offset = T,
  beta_prior = "cauchy",
  small_area_prior = "BYM2",
  intercept_scale = 10,
  large_area_prior = "random",
  iter = 25000,
  warmup = 22500,
  thin = 4,
  cores = 4,
  chains = 4,
  control = list(max_treedepth = 25, adapt_delta = 0.99),
  verbose = T
)
```
